---
title: "sharereward_figures"
author: "Jen Yang"
date: "2025-10-29, last modified 2025-10-29"
output:
  word_document:
    toc: true
    toc_depth: '6'
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

# Load libraries
```{r libraries, message=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(magrittr)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(interactions)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(jsonlite)
library(rjson)
library(readr)
library(rstan)
library(easystats)
library(patchwork)
library(brms)
```

# define dir and load data
```{r}
# gitrepo_path = here() # find repo path
gitrepo_path = "/Users/momocco/Documents/GitHub/rf1-sra-sharedreward/blobs_jen"

code_dir = paste(gitrepo_path, "code", sep = "/")
data_dir = paste(gitrepo_path, "data", sep = "/")
figure_dir = paste(gitrepo_path, "figure", sep = "/")
```

# Cooper's code, for model checking
```{r}
# ppi_VS-VS_c14_age-effect

# DV = `ppi_VS.VS_c14_2mm_model.Fwin.Floss_Swin.Sloss_type.ppi_seed.VS_cope.14_cname.rew.pun_F.S`

# IV focal = age_demeaned

# IV control = 
# avg_tsnr_demeaned
# avg_fdmean_demeaned
# flip_demeaned
# study_demeaned
# Fwin_minus_Floss_minus_Swin_minus_Sloss_z_demeaned
# age_x_Fwin_minus_Floss_minus_Swin_minus_Sloss_z_demeaned

# weights = `weights_var_ppi_VS-VS_c14_2mm_model.Fwin.Floss_Swin.Sloss_type.ppi_seed.VS_cope.14_cname.rew.pun_F.S`)
```

# load data
```{r}
csv_name = "jen-SRaging.csv"
raw_df = read.csv(paste(data_dir, csv_name, sep = "/"),
                  header = T)

plot_df = raw_df %>% 
  mutate(weights = 1/`var_ppi_VS.VS_c14_2mm_model.Fwin.Floss_Swin.Sloss_type.ppi_seed.VS_cope.14_cname.rew.pun_F.S`) %>% 
  rename(
    DV = `ppi_VS.VS_c14_2mm_model.Fwin.Floss_Swin.Sloss_type.ppi_seed.VS_cope.14_cname.rew.pun_F.S`,
    IV_focal = age_demeaned,
    ctrl_tsnr = avg_tsnr_demeaned,
    ctrl_fdmean = avg_fdmean_demeaned,
    ctrl_study = study_demeaned,
    ctrl_flip = flip_demeaned,
    ctrl_z_1 = Fwin_minus_Floss_minus_Swin_minus_Sloss_z_demeaned,
    ctrl_z_2 = age_x_Fwin_minus_Floss_minus_Swin_minus_Sloss_z_demeaned) %>% 
  mutate(DV_norm = DV/sd(DV),
         IV_focal_norm = IV_focal/sd(IV_focal)) %>% 
  select(DV, DV_norm,
         IV_focal, IV_focal_norm,
         ctrl_tsnr, ctrl_fdmean, ctrl_study, ctrl_flip, ctrl_z_1, ctrl_z_2, 
         weights) 
```

# stats check
```{r}
VS_VS_m_r_wls = lm(DV ~ IV_focal +
                     ctrl_tsnr + ctrl_fdmean + ctrl_study + ctrl_flip + ctrl_z_1 + ctrl_z_2,
                   data = plot_df, weights = plot_df$weights)
summary(VS_VS_m_r_wls)

# VS_VS_m_r_ols = lm(DV ~ IV_focal +
#                      ctrl_tsnr + ctrl_fdmean + ctrl_study + ctrl_flip + ctrl_z_1 + ctrl_z_2,
#                    data = plot_df)
# summary(VS_VS_m_r_ols)
```

# figure, without controls
```{r}
ggplot(plot_df, aes(x = IV_focal, y = DV)) +
  # Plot the partial residuals. We can still map size to the original weights.
  geom_point(aes(size = weights),
             color = "darkgreen", alpha = 0.7) +
  # Add a weighted regression line through the partial residuals.
  # The slope of this line is the partial coefficient of X.
  geom_smooth(method = "lm", 
              aes(weight = weights), 
              color = "black", se = T)
```


# figure, with controls
## data prep
```{r}
# Calculate the partial component from DV
beta_IV_focal_wls = coef(VS_VS_m_r_wls)["IV_focal"]
plot_df$DV_partial_component <- 
  residuals(VS_VS_m_r_wls) + (beta_IV_focal_wls * plot_df$IV_focal)
```

## coef verification
```{r}
# verify coef
verification_model <- lm(DV_partial_component ~ IV_focal, 
                         data = plot_df, weights = weights)
summary(verification_model)

coef(VS_VS_m_r_wls)["IV_focal"] == coef(verification_model)["IV_focal"]

# note that se, t, and p are all different! this is why the se is turned of in geom_smooth because it does not represent the correct se. only the slope is correct!
```
## prepare se
```{r}
# create simulated data
sim_df <- data.frame(
  IV_focal = seq(min(plot_df$IV_focal), max(plot_df$IV_focal), length.out = 100),
  ctrl_tsnr = median(plot_df$ctrl_tsnr),
  ctrl_fdmean = median(plot_df$ctrl_fdmean),
  ctrl_study = median(plot_df$ctrl_study),
  ctrl_flip = median(plot_df$ctrl_flip),
  ctrl_z_1 = median(plot_df$ctrl_z_1),
  ctrl_z_2 = median(plot_df$ctrl_z_2))

sim_predictions <- predict(VS_VS_m_r_wls, newdata = sim_df, interval = "confidence")
sim_df <- cbind(sim_df, as.data.frame(sim_predictions))
```


## plot using predicted y for correct slope and se. y axis is the original 
(Adjusted Prediction Plot)
```{r}
ggplot() +
  # original data points with weights represented by size
  geom_point(data = plot_df, 
             aes(x = IV_focal, y = DV, 
                 size = weights,
                 color = "darkgreen"),
             alpha = 0.7) +
  # se using simulated data
  geom_ribbon(data = sim_df, 
              aes(x = IV_focal, ymin = lwr, ymax = upr), 
              fill = "skyblue", alpha = 0.4) +
  # line with partial coef
  geom_line(data = sim_df, aes(x = IV_focal, y = fit), color = "blue", linewidth = 1.1)
```

# plot using partial residual of DV as y axis and original IV_focal as x axis
(Adjusted Prediction Plot)
(in OLS the x axis should be partial residual of IV_focal, which is different from WSL)
```{r}
ggplot() +
  # original data points with weights represented by size
  geom_point(data = plot_df, 
             aes(x = IV_focal, y = DV_partial_component, 
                 size = weights,
                 color = "darkgreen"),
             alpha = 0.7) +
  # line with partial coef
  geom_smooth(data = plot_df,
              aes(x = IV_focal, y = DV_partial_component,
                  weight = weights),
              color = "red",
              method = "lm", 
              se = F) +# this se is WRONG and therefore must be turned off!
  # compare with the line generated from sim data
  ## se using simulated data
  geom_ribbon(data = sim_df,
              aes(x = IV_focal, ymin = lwr, ymax = upr),
              fill = "darkgreen", alpha = 0.4) +
  geom_line(data = sim_df, aes(x = IV_focal, y = fit), color = "darkgreen", linewidth = 1.1)
```

# get the intercept change resultsed from controls
```{r}
beta_0 <- coef(VS_VS_m_r_wls)["(Intercept)"]
beta_ctrl_tsnr = coef(VS_VS_m_r_wls)["ctrl_tsnr"]
beta_ctrl_fdmean = coef(VS_VS_m_r_wls)["ctrl_fdmean"]
beta_ctrl_study = coef(VS_VS_m_r_wls)["ctrl_study"]
beta_ctrl_flip = coef(VS_VS_m_r_wls)["ctrl_flip"]
beta_ctrl_z_1 = coef(VS_VS_m_r_wls)["ctrl_z_1"]
beta_ctrl_z_2 = coef(VS_VS_m_r_wls)["ctrl_z_2"]

diff_intercept = 
  beta_0 +
  beta_ctrl_tsnr * median(plot_df$ctrl_tsnr) + 
  beta_ctrl_fdmean * median(plot_df$ctrl_fdmean) + 
  beta_ctrl_study * median(plot_df$ctrl_study) + 
  beta_ctrl_flip * median(plot_df$ctrl_flip) +
  beta_ctrl_z_1 * median(plot_df$ctrl_z_1) + 
  beta_ctrl_z_2 * median(plot_df$ctrl_z_2)

```

# combining adjusted predicted value plot with partial residual plot
(right slope, righte se, partial DV)
```{r}
ggplot() +
  # original data points with weights represented by size
  geom_point(data = plot_df, 
             aes(x = IV_focal, y = DV_partial_component, 
                 size = weights,
                 color = "darkgreen"),
             alpha = 0.7) +
  # line with partial coef
  geom_smooth(data = plot_df,
              aes(x = IV_focal, y = DV_partial_component,
                  weight = weights),
              color = "red",
              method = "lm", 
              se = F) +# this se is WRONG and therefore must be turned off!
  # compare with the line generated from sim data
  ## se using simulated data
  geom_ribbon(data = sim_df,
              aes(x = IV_focal, 
                  ymin = lwr - diff_intercept, 
                  ymax = upr - diff_intercept),
              fill = "darkgreen", alpha = 0.4)
  # geom_line(data = sim_df, aes(x = IV_focal, y = fit), color = "darkgreen", linewidth = 1.1)
```
```


# end of code

