---
title: "sharereward_figures"
author: "Jen Yang"
date: "2025-10-29, last modified 2025-10-30"
output:
  word_document:
    toc: true
    toc_depth: '6'
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

# Load libraries
```{r libraries, message=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(magrittr)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(interactions)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(jsonlite)
library(rjson)
library(readr)
library(rstan)
library(easystats)
library(patchwork)
library(brms)
```

# define dir and load data
```{r}
# gitrepo_path = here() # find repo path
gitrepo_path = "/Users/momocco/Documents/GitHub/rf1-sra-sharedreward/blobs_jen"

code_dir = paste(gitrepo_path, "code", sep = "/")
data_dir = paste(gitrepo_path, "data", sep = "/")
figure_dir = paste(gitrepo_path, "figure", sep = "/")
```

# Cooper's code, for model checking
```{r}
# ppi_VS-VS_c14_age-effect

# from Cooper
## model3 <- lm(`ppi_VS.VS_c14_2mm_model.Fwin.Floss_Swin.Sloss_type.ppi_seed.VS_cope.14_cname.rew.pun_F.S` ~ age_demeaned + avg_tsnr_demeaned + avg_fdmean_demeaned + flip_demeaned + study_demeaned + Fwin_minus_Floss_minus_Swin_minus_Sloss_z_demeaned + age_x_Fwin_minus_Floss_minus_Swin_minus_Sloss_z_demeaned, data = df, weights = `weights_var_ppi_VS-VS_c14_2mm_model.Fwin.Floss_Swin.Sloss_type.ppi_seed.VS_cope.14_cname.rew.pun_F.S`)

# inventry

## DV = `ppi_VS.VS_c14_2mm_model.Fwin.Floss_Swin.Sloss_type.ppi_seed.VS_cope.14_cname.rew.pun_F.S`

## IV focal = age_demeaned

## IV control = 
## avg_tsnr_demeaned
## avg_fdmean_demeaned
## flip_demeaned
## study_demeaned
## Fwin_minus_Floss_minus_Swin_minus_Sloss_z_demeaned
# age_x_Fwin_minus_Floss_minus_Swin_minus_Sloss_z_demeaned

## weights = `weights_var_ppi_VS-VS_c14_2mm_model.Fwin.Floss_Swin.Sloss_type.ppi_seed.VS_cope.14_cname.rew.pun_F.S`)
```

# prepare data
```{r}
csv_name = "jen-SRaging.csv"
raw_df = read.csv(paste(data_dir, csv_name, sep = "/"),
                  header = T)

plot_df = raw_df %>% 
  mutate(weights = 1/`var_ppi_VS.VS_c14_2mm_model.Fwin.Floss_Swin.Sloss_type.ppi_seed.VS_cope.14_cname.rew.pun_F.S`) %>% 
  rename(
    DV = `ppi_VS.VS_c14_2mm_model.Fwin.Floss_Swin.Sloss_type.ppi_seed.VS_cope.14_cname.rew.pun_F.S`,
    IV_focal = age_demeaned,
    ctrl_tsnr = avg_tsnr_demeaned,
    ctrl_fdmean = avg_fdmean_demeaned,
    ctrl_study = study_demeaned,
    ctrl_flip = flip_demeaned,
    ctrl_z_1 = Fwin_minus_Floss_minus_Swin_minus_Sloss_z_demeaned,
    ctrl_z_2 = age_x_Fwin_minus_Floss_minus_Swin_minus_Sloss_z_demeaned) %>% 
  mutate(DV_norm = DV/sd(DV),
         IV_focal_norm = IV_focal/sd(IV_focal)) %>% 
  select(DV, DV_norm,
         IV_focal, IV_focal_norm,
         ctrl_tsnr, ctrl_fdmean, ctrl_study, ctrl_flip, ctrl_z_1, ctrl_z_2, 
         weights) 
```

# stats check
```{r}
# withOUT weight
VS_VS_m_r_ols = lm(DV ~ IV_focal +
                     ctrl_tsnr + ctrl_fdmean + ctrl_study + ctrl_flip + ctrl_z_1 + ctrl_z_2,
                   data = plot_df)
summary(VS_VS_m_r_ols)

full_summary = summary(VS_VS_m_r_ols)

# WITH weight
## full model
VS_VS_m_r_wls = lm(DV ~ IV_focal +
                     ctrl_tsnr + ctrl_fdmean + ctrl_study + ctrl_flip + ctrl_z_1 + ctrl_z_2,
                   data = plot_df, weights = plot_df$weights)
summary(VS_VS_m_r_wls)

full_summary = summary(VS_VS_m_r_wls)
r2_full_adj = full_summary$adj.r.squared
r2_full = full_summary$r.squared

## reduced model
VS_VS_m_r_wls_null = lm(DV ~
                          ctrl_tsnr + ctrl_fdmean + ctrl_study + ctrl_flip + ctrl_z_1 + ctrl_z_2,
                        data = plot_df)
# summary(VS_VS_m_r_wls_null)

reduced_summary = summary(VS_VS_m_r_wls_null)
r2_reduced_adj = reduced_summary$adj.r.squared
r2_reduced = reduced_summary$r.squared

# Cohen's f squared
(r2_full_adj-r2_reduced_adj)/(1-r2_full_adj)

(r2_full-r2_reduced)/(1-r2_full)
```

# figure, with controls
## data prep
```{r}
# Calculate the partial component from DV
beta_IV_focal_wls = coef(VS_VS_m_r_wls)["IV_focal"]
plot_df$DV_partial_component <- 
  residuals(VS_VS_m_r_wls) + (beta_IV_focal_wls * plot_df$IV_focal)
```

## coef verification
```{r}
# verify coef
verification_model <- lm(DV_partial_component ~ IV_focal, 
                         data = plot_df, weights = weights)
summary(verification_model)

coef(VS_VS_m_r_wls)["IV_focal"] == coef(verification_model)["IV_focal"]

# note that se, t, and p are all different! this is why the se is turned of in geom_smooth because it does not represent the correct se. only the slope is correct!
```

## prepare se
```{r}
# create simulated data
sim_df <- data.frame(
  IV_focal = seq(min(plot_df$IV_focal), max(plot_df$IV_focal), length.out = 100),
  ctrl_tsnr = median(plot_df$ctrl_tsnr),
  ctrl_fdmean = median(plot_df$ctrl_fdmean),
  ctrl_study = median(plot_df$ctrl_study),
  ctrl_flip = median(plot_df$ctrl_flip),
  ctrl_z_1 = median(plot_df$ctrl_z_1),
  ctrl_z_2 = median(plot_df$ctrl_z_2))

sim_predictions <- predict(VS_VS_m_r_wls, newdata = sim_df, interval = "confidence")
sim_df <- cbind(sim_df, as.data.frame(sim_predictions))
```


## plot using predicted y for correct slope and se. y axis is the original 
(Adjusted Prediction Plot)
```{r}
ggplot() +
  # original data points with weights represented by size
  geom_point(data = plot_df, 
             aes(x = IV_focal, y = DV, 
                 size = weights),
             alpha = 0.7) +
  # se using simulated data
  geom_ribbon(data = sim_df, 
              aes(x = IV_focal, ymin = lwr, ymax = upr), 
              fill = "skyblue", alpha = 0.4) +
  # line with partial coef
  geom_line(data = sim_df, aes(x = IV_focal, y = fit), color = "darkred", linewidth = 1.1)
```

## plot using partial residual of DV as y axis and original IV_focal as x axis
(Adjusted Prediction Plot)
(in OLS the x axis should be partial residual of IV_focal, which is different from WSL)
```{r}
ggplot() +
  # original data points with weights represented by size
  geom_point(data = plot_df, 
             aes(x = IV_focal, y = DV_partial_component, 
                 size = weights),
             alpha = 0.7) +
  # line with partial coef
  geom_smooth(data = plot_df,
              aes(x = IV_focal, y = DV_partial_component,
                  weight = weights),
              color = "red",
              method = "lm", 
              se = F) +# this se is WRONG and therefore must be turned off!
  # compare with the line generated from sim data
  ## se using simulated data
  geom_ribbon(data = sim_df,
              aes(x = IV_focal, ymin = lwr, ymax = upr),
              fill = "darkgreen", alpha = 0.4) +
  geom_line(data = sim_df, aes(x = IV_focal, y = fit), color = "darkgreen", linewidth = 1.1)
```

# get the intercept change resultsed from controls
```{r}
beta_0 <- coef(VS_VS_m_r_wls)["(Intercept)"]
beta_ctrl_tsnr = coef(VS_VS_m_r_wls)["ctrl_tsnr"]
beta_ctrl_fdmean = coef(VS_VS_m_r_wls)["ctrl_fdmean"]
beta_ctrl_study = coef(VS_VS_m_r_wls)["ctrl_study"]
beta_ctrl_flip = coef(VS_VS_m_r_wls)["ctrl_flip"]
beta_ctrl_z_1 = coef(VS_VS_m_r_wls)["ctrl_z_1"]
beta_ctrl_z_2 = coef(VS_VS_m_r_wls)["ctrl_z_2"]

diff_intercept = 
  beta_0 +
  beta_ctrl_tsnr * median(plot_df$ctrl_tsnr) + 
  beta_ctrl_fdmean * median(plot_df$ctrl_fdmean) + 
  beta_ctrl_study * median(plot_df$ctrl_study) + 
  beta_ctrl_flip * median(plot_df$ctrl_flip) +
  beta_ctrl_z_1 * median(plot_df$ctrl_z_1) + 
  beta_ctrl_z_2 * median(plot_df$ctrl_z_2)

```

# figure param setup
```{r}
axis_title = 12
axis_ticks = 10
axis_text = 12
axis_label = 12

legend_all = 12

annotate_text = 4
axis_line_width = 1/1.5
fit_line_width = 2
zero_line_width = 0.6
path_line_width = 0.5

data_point_alpha = 0.5
data_point_size = 1
path_line_alpha = 0.6

mean_point_size = 3

line_width = 1
point_size = 3

summary_point_alpha = 1
summary_point_size = 3

annotate_text = 4

smooth_alpha = 0.3

w = 3.4
h = 3.4

# color_Stranger = "#ee964b"
# color_Friend = "#118ab2"
# 
# color_Trust = "#2a9d8f"
# color_NotTrust = "#d8315b"
# 
# color_age = "#0b6e4f"
# color_In_Im = "#592e83"
```

# plot that combines adjusted predicted value plot with partial residual plot
(right slope, righte se, partial DV)
```{r}
vs_vs_p = 
  ggplot() +
  # original data points with weights represented by size
  geom_point(data = plot_df, 
             aes(x = IV_focal, y = DV_partial_component, 
                 size = weights),
             color = "skyblue",
             alpha = 0.5) +
  # line with partial coef
  geom_smooth(data = plot_df,
              aes(x = IV_focal, y = DV_partial_component,
                  weight = weights),
              color = "darkred",
              method = "lm", 
              se = F) +# this se is WRONG and therefore must be turned off!
  # compare with the line generated from sim data
  ## se using simulated data
  geom_ribbon(data = sim_df,
              aes(x = IV_focal, 
                  ymin = lwr - diff_intercept, 
                  ymax = upr - diff_intercept),
              fill = "darkred", alpha = 0.4) + 
  labs(x = "age (demeaned)", 
       y = "brain, partial residual",
       color = NULL,
       fill = NULL) +
  theme(axis.line = 
          element_line(linewidth = 1, 
                       colour = "black", 
                       linetype=1),
        axis.text.x = element_text(size = axis_text), 
        axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face="bold"), 
        axis.title.y = element_text(size = axis_title, face="bold"),
        panel.grid.minor = element_blank()
        # legend.position = c(0.8, 0.8)
  )
# geom_line(data = sim_df, aes(x = IV_focal, y = fit), color = "darkgreen", linewidth = 1.1)

vs_vs_p
```

# save plot
```{r}
ggsave(paste(figure_dir, "VS-VS_wls.png", sep = "/"),
       vs_vs_p, 
       width = w*1.5, height = h,
       unit = "in", dpi=300)
```


# end of code

